Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/evaluation.tex
Results almost there.

\begin{table}[t]
\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla K40 GPU).}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

\paragraph{Novice Study Design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}. All twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.

\paragraph{Expert Study Design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

>>>>

\begin{table}[t]
\caption{Training parameters, cost, and results of our guided proofreading classifier versus focused proofreading by Plaza~\cite{focused_proofreading}. Both methods were trained on the same mouse brain dataset using the same hardware (Tesla X GPU).}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

\paragraph{Novice study design.} We recruited participants with no experience in electron microscopy data or proofreading, through flyers, mailing lists, and personal interaction. Based on sample size calculation theory, we estimated the study needed ten users per proofreading tool including four potential dropouts~\cite{samplesize1,samplesize2}. All twenty participants completed the study ($N=20$, 10 female; 19-65 years old, $M$=30).

Each study session began with a five minute standardized explanation of the task. Then, the participants were asked to perform a 3 minute proofreading task on separate but representative data using focused proofreading. The participants were allowed to ask questions during this time. The classifier did not matter in this case since the user interface was the same. The experimenter then loaded the AC4 subvolume with initial pre-computed classifications by either guided proofreading or focused proofreading depending on assignment. After 30 minutes, the participants completed the raw NASA-TLX standard questions for task evaluation~\cite{NASATLX}.
\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with less corrections.}
\label{fig:ac4trails}
\end{figure*}
\paragraph{Expert study design.} We recruited 4 domain experts to evaluate the performance of both guided and focused proofreading. We obtained study consent and randomly assigned 2 experts to proofread using each classifier. The experts performed the 3 minute test run on different data prior to proofreading for 30 minutes. After the task ended, the experts were asked to complete the raw NASA-TLX questionnaire.

### 2016-11-15 paper/results.tex
Results almost there.

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with less corrections.}
\label{fig:ac4trails}
\end{figure*}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
\label{fig:ac4trails}
\end{figure}

@@

\subsection{Selection Oracle}
Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets. This is not surprising since all detected merge and split are corrected if they are good corrections.

\subsection{Automatic Method}

\subsection{Force Choice User Experiment}

The initial segmentation for AC4 had a VI of XXX.

\textbf{Novice Performance.} 
\\~\\
\textbf{Expert Performance.}
\\~\\
\textbf{Subjective Responses.} All subjective responses were recorded using the NASA-TLX workload index. The workload index asks study participants to state their mental, physical, temporal demands, as well as rate their performance, effort, and frustration on a scale with 21 graduations. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is not surprising since the user interface was the same for both control groups.

>>>>

@@

\subsection{Classifier Comparison}

We compare the guided proofreading and focused proofreading classifiers and report precision/recall as well as f1 scores across datasets.

\paragraph{L. Cylinder.} Evaluation was performed on previously unseen sections of mouse cortex volume of Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches in respect to the ground truth labeling. We then ranked each patch using focused proofreading and guided proofreading and compared precision/recall (Table \ref{tab:prcyl}. Our method exhibits higher precision and recall for correct and error patches.

\begin{table}[h]
\caption{Classifier comparison on an unbalanced test set of the L. Cylinder volume.}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{l|c|c|c|c}

 & precision & recall & f1 score & \# \\ 
\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 0.93 & 0.31 & 0.47 & 81,184 \\ 
split error & 0.11 & 0.78 & 0.19 & 8,780 \\ 
\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.93 & 0.96 & 81,184 \\ 
split error & 0.61 & 0.96 & 0.74 & 8,780 \\ 
\end{tabular} 
}
\label{tab:prcyl}
\end{table}

\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Again, guided proofreading achieves better precision/recall scores (Table \ref{tab:prac4}).

\begin{table}[h]
\caption{Classifier comparison on correct and split error patches of the AC4 subvolume.}%While the training of our classifier is more expensive, testing accuracy is superior. }

\small{
\begin{tabular}{l|c|c|c|c}

 & precision & recall & f1 score & \# \\ 
\textbf{Focused Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 0.94 & 0.69 & 0.80 & 3,488 \\ 
split error & 0.14 & 0.51 & 0.21 & 332 \\ 
\textbf{Guided Proofreading} & ~ & ~ & ~ & ~ \\ 
correct & 1.00 & 0.92 & 0.96 & 3,488 \\ 
split error & 0.54 & 0.95 & 0.69 & 332 \\ 
\end{tabular} 
}
\label{tab:prac4}
\end{table}

\subsection{Forced Choice User Experiment}
We performed a user study to evaluate the forced choice error correction method among novices and experts. To perform a reasonable experiment and be comparable to Haehn's~\etal Dojo user study, participants were asked to proofread the AC4 subvolume for 30 minutes. Even with computer-aided proofreading methods, correcting the whole volume in this time frame is simply not possible. We counted 10 merge errors and 322 split errors by computing the maximum overlap of the initial segmentation and the ground truth labeling (both provided by Haehn~\etal). For evaluation, we measure the performance of proofreading quantitatively by comparing VI scores of proofread segmentations against the ground truth labelings. The median VI of the initial segmentation in respect to ground truth was 0.476 (SD=0.089). Most novices and all experts were able to improve this with focused proofreading and guided proofreading (Fig.~\ref{fig:ac4trails}).

\paragraph{Novice performance.} Participants using focused proofreading were able to reduce the median VI of the automatic segmentation to 0.469 (SD=0.87). On average, users viewed 423.4 corrections and accepted 45.8 of them with an average time of 4.9 seconds spent per correction. Participants using guided proofreading were able to reduce the median VI to 0.424 (SD=0.037). Here, users viewed 353.4 corrections on average and accepted 106.9 in 6.2 seconds. While three users of focused proofreading made the initial segmentation worse, all participants using guided proofreading were able to improve it. In comparison to the results of Haehn~\etal, focused and guided proofreading outperform interactive proofreading with Dojo. The slope of VI per correction in Fig.~\ref{fig:ac4trails} shows that guided proofreading enables VI changes with fewer corrections. Interestingly, the performance decreases after approximately 300 corrections. There are two explanations for this: user fatigue and increasing uncertainty during error suggestion from the classifier. Regarding fatigue, we suggest for future experiments to add short breaks after every ten minutes.

\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases. With focused proofreading, the median VI of the automatic segmentation was 0.439 (SD=0.084). With guided proofreading, the median VI was 0.396 (SD=0.032) as shown in Fig.~\ref{fig:ac4boxplot}.

\paragraph{Subjective responses.} All subjective responses were recorded using the NASA-TLX workload index. Mental, physical, and temporal demands were reported slightly higher for participants using focused proofreading. However, these differences were not statistically significant. This is not surprising since the user interface was the same for both control groups.

\subsection{Automatic Error Correction}

\paragraph{Selection Oracle.} Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets. This is not surprising since all detected merge and split are corrected if the segmentation is improved. Fig.~\ref{fig:ac4trails} shows slope of VI reduction using the selection oracle on the AC4 subvolume. With focused proofreading, the selection oracle reaches a median VI of 0.353 (SD=0.037) after 1605 corrections. With guided proofreading, the oracle reaches a median VI of 0.342 (SD=0.03) after approximately 800 corrections and then stagnates until all regions are proofread. Both results are very close to the best possible median VI of 0.334 which we calculated by computing maximum overlap with the ground truth. The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires less corrections to reach a reasonable reduction in VI on the AC4 subvolume and Fig.~\ref{fig:ac4boxplot} shows the distribution.
The results on the L. Cylinder dataset (initial VI XX (SD=YY) are similar: Focused proofreading reduces the median VI to XX (SD=YY) after 26,170 corrections. Guided proofreading reduces the median VI to XX (SD=YY) after XX corrections.

\paragraph{Automatic Method.}

\subsection{Merge vs. Split Error Detection}

\subsection{Limitations}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
\label{fig:ac4boxplot}
\end{figure}
